Using Camera Traps and Computer Vision to Quantify Wildlife Diversity and Co-Occurrence across \nOntario’s Far North

### 2023-10-17 analysis/paper/paper.qmd
update paper

```{r}
# library(forcats)
# anns_wide_animals_joined_mut %>% 
#   ggplot(aes(x=date_time, y=species)) + geom_point()
# anns_wide_animals_joined_mut %>% 
#   dplyr::filter(species == "Fisher") %>% View()

@@

```{r}
for_vic <- anns_wide_animals_joined_mut %>% 
  dplyr::select(id,species,date_time, camera_id) %>% 
  dplyr::left_join(cams_sf %>% dplyr::select(camera_id, plot_id) %>% sf::st_drop_geometry(),
                   by = "camera_id")
tot_camera <- for_vic$camera_id %>% unique() %>% length()
hit_rates <- for_vic %>% dplyr::select(species, camera_id) %>% 
  dplyr::group_by(species) %>% dplyr::summarise(n_cameras=length(unique(camera_id))) %>% 
  dplyr::ungroup() %>% dplyr::mutate(rate = n_cameras/tot_camera*100) %>% 
  dplyr::arrange(dplyr::desc(rate))
# det_history_two_weeks <-

>>>>

```{r eval=FALSE}
# library(forcats)
library(ggplot2)
# anns_wide_animals_joined_mut %>% 
#   ggplot(aes(x=date_time, y=species)) + geom_point()
# anns_wide_animals_joined_mut %>% 
#   dplyr::filter(species == "Fisher") %>% View()

@@

```{r eval=FALSE}
for_vic <- anns_wide_animals_joined_mut %>% 
  dplyr::select(id,species,date_time, camera_id) %>% 
  dplyr::left_join(cams_sf %>% dplyr::select(camera_id, plot_id) %>% sf::st_drop_geometry(),
                   by = "camera_id")
tot_camera <- for_vic$camera_id %>% unique() %>% length()
hit_rates <- for_vic %>% dplyr::select(species, camera_id) %>% 
  dplyr::group_by(species) %>% dplyr::summarise(n_cameras=length(unique(camera_id))) %>% 
  dplyr::ungroup() %>% dplyr::mutate(rate = n_cameras/tot_camera*100) %>% 
  dplyr::arrange(dplyr::desc(rate))
# det_history_two_weeks <-
